\Large The user manual: flavor Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-06-08 doc/FAS-GLoBES.tex
update manuscript

%\usepackage{underscore}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[nottoc]{tocbibind}

@@

In the following, we give more details about using \textbf{FASE-GLoBES}. In Sec.~\ref{sec:download}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}. Then, in Sec.~\ref{sec:compile}, we will introduce how to compile and run the code. More complicated is setting the model, and the way to do this will be described in Sec.~\ref{sec:model_set}. Finally, we will discuss how to set up the prior in Sec.~\ref{sec:prior}.

\subsection{Download and Installation}\label{sec:download}
\textbf{download and install GLoBES and FASE-GLoBES}\\
{\color{red}[will fill in after the code ready on Github]}

\subsection{Compile and Run}\label{sec:compile}
As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}. To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input.o\\
	gcc my\_program.o  FASE\_GLoBES.o model-input.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\vspace{0.2cm}\\	
where \texttt{\{compile\_execusion\}} is the makefile commend for the program \texttt{my\_program.o} and the execution \texttt{my\_executable} is the output. After giving this script in the \textbf{GLoBES} \texttt{Makefile}, the user needs to makefile the program \texttt{my\_program} on the terminal.\vspace{0.2cm}\\
\texttt{makefile \{makefile\_execution\}}\vspace{0.2cm}\\
And, the user can execute the program by typing the following commend on the terminal.\vspace{0.2cm}\\ 
\texttt{./my\_executable}%\vspace{0.2cm}\\

@@

Finally we need to initialize \textbf{FaSE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
\texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\

@@

{\color{blue}In the following, all examples are mainly presented for TDLS, except for Sec.~\ref{sec:ex_MT}. However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavor model. We therefore in the \textbf{FaSE} distribution, show the warped flavor symmetry (WSF)~\cite{Chen:2015jta}, trimaximal mixing sum rule (TM1)~\cite{Albright:2008rp}  as examples, which will not be further introduced in this manual.
}

>>>>

%\usepackage{underscore}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[nottoc]{tocbibind}

@@

In the following, we give more details about using \textbf{FASE-GLoBES}. In Sec.~\ref{sec:compile}, we will give the instruction to download and install \textbf{GLoBES} and \textbf{FASE}, and we will introduce how to compile and run the code. More complicated is setting the model, and the way to do this will be described in Sec.~\ref{sec:model_set}. Finally, we will discuss how to set up the prior in Sec.~\ref{sec:prior}.

\subsection{Download, compile and run}\label{sec:compile}
{\color{blue}

The user can download \textbf{FaSE} simply from \url{https://github.com/tcwphy/FASE_GLoBES.git} directly. Or, the user can also download it with 
\begin{verbatim}
git clone https://github.com/tcwphy/FASE_GLoBES.git
\end{verbatim}
}

As \textbf{FaSE} works based on \textbf{GLoBES}, the user should use the \textbf{GLoBES} \texttt{Makefile}, but include the binary file of \textbf{FaSE}. To do so, we include the script in the \texttt{Makefile},\vspace{0.2cm}\\
\texttt{\{makefile\_execution\}: my\_program.o  FASE\_GLoBES.o model-input.o\\
	gcc my\_program.o  FASE\_GLoBES.o model-input.o -o my\_executable  \$(LDFLAGS) \$(local\_LDFLAGS)}\vspace{0.2cm}\\	
where \texttt{\{compile\_execusion\}} is the makefile commend for the program \texttt{my\_program.o} and the execution \texttt{my\_executable} is the output. After giving this script in the \textbf{GLoBES} \texttt{Makefile}, the user needs to makefile the program \texttt{my\_program} on the terminal.\vspace{0.2cm}\\
\texttt{makefile \{makefile\_execution\}}\vspace{0.2cm}\\
And, the user can execute the program by typing the following commend on the terminal.\vspace{0.2cm}\\ 
\texttt{./my\_executable}%\vspace{0.2cm}\\

@@

Finally we need to initialize \textbf{FaSE} by giving $N_{para}$ which is the number of model parameters. To do so, we need to include the following script in the main code.\\
\texttt{    MODEL\_init($N_{para}$); }\vspace{0.2cm}\\ 
We note that $N_{para}$ should not be larger than the number of standard oscillation parameters, $6$.

@@

{\color{blue}In the following, all examples are mainly presented for TDLS, except for Sec.~\ref{sec:ex_MT}. However, we remind the user that though we use TDLS as an example, \textbf{FaSE-GLoBES} should not be limited in any flavor model. We therefore in the \textbf{FaSE} distribution, show the warped flavor symmetry (WSF)~\cite{Chen:2015jta}, trimaximal mixing sum rule (TM1)~\cite{Albright:2008rp} as examples, which will not be further introduced in this manual. We summarise our examples for \textbf{FaSE-GLoBES} and references for those theoretical models in Tabl~\ref{tab:examples}. And in the rest of this section, we demonstrate the \textbf{example 1} and \textbf{example 4}. 
}

\begin{table}[h!]
\caption{\label{tab:examples}Summary of available AEDL files for some of most-discussed experiments.}
\centering
\begin{tabular}{c|c|c|c}
example   & model & application & reference \\\hline\hline
\textbf{example1}    &  TDLS  & parameter constraint & \cite{King:2013iva,King:2015dvf,King:2016yvg} \\
\textbf{example2}    &  WSF  & parameter constraint & \cite{Chen:2015jta} \\
\textbf{example3}    &  TM1 sum rule  & model testing & \cite{Albright:2008rp} \\
\textbf{example4}    &  $S_4$ modular  & model testing &\cite{deMedeirosVarzielas:2019cyj}  \\
\end{tabular}
\end{table}
